Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-10 delegations.tex
Change wording
Remove TODO
Change definition of delegation schemes

\begin{definition}
	A \emph{quantum delegation protocol} is an polynomial-round interactive protocol between a BPP verifier and a BQP prover. The BPP verifier has an arbitrary quantum circuit with classical input that it needs to evaluate with the help of the prover.
\end{definition}

TODO (maybe don't assume universality?)

\begin{definition}
	A quantum delegation protocol has \emph{long output with error $\epsilon$} if the output can have multiple bits. In this case, the verifier should end with a measurement result of the output register. Said result's probability distribution would be within $\epsilon$ of the true distribution.
\end{definition}

@@

\begin{definition}
	A quantum delegation protocol is \emph{verifiable} if the verifier can check if the output is correct. TODO need to be more rigorous here.
\end{definition}

>>>>

\begin{definition}
	A \emph{quantum delegation protocol} is an polynomial-round interactive protocol between a BPP verifier and a BQP prover. The BPP verifier has an arbitrary quantum circuit with classical input that it needs to evaluate and measure the result by interacting with the prover.
\end{definition}

\begin{definition}
	A quantum delegation protocol has \emph{long output} if the output can have multiple bits. In this case, the verifier should end with a measurement result of the output register.
\end{definition}

@@

\begin{definition}
	A quantum delegation protocol is \emph{$\delta,\epsilon$-verifiable} if the verifier's output distribution is within $\delta$ of the true distribution whenever it interacts with a prover whose probability to be accepted is greater than $\epsilon$.
\end{definition}
